---
title: "Statistical Inference"
author: "Alexander Klonov"
date: "07 09 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

This task requires to do some explanatory analysis and make conclusions about data we have. The data for task is ToothGrowth 

## Explanotory analysis

First we need to load data:
```{r}
data(ToothGrowth)
library(ggplot2)
```
Look for dimensions and collum names:
```{r}
dim(ToothGrowth)
names(ToothGrowth)
head(ToothGrowth)
```
And finally let's look through summary
```{r}
summary(ToothGrowth)
```

### Quick graphs

To finish explanatory analyses, we need to build up a couple graphs. First will be a graph showing conection between supplement type and teeth length.

```{r}
g<-ggplot(data = ToothGrowth, aes(len, colour = supp))+geom_boxplot()
g+ggtitle("Connection between different supplement and length")
```

And then let's add more data to this graph to see if there any connection between dose and teeth length.

```{r}
g<-ggplot(data= ToothGrowth, aes(len, dose, shape = supp, col = supp))+
  geom_point(size = 4)+
  facet_grid(supp~.)
g+
  ggtitle("Connection between doses and teeth length based on the supplements")+
  geom_smooth(method = "lm")
```

### Statistical inference 

Let's assume that type of the supplement doesn't affect teeth length. To reject or fail to reject this theory let's conduct a t test.

```{r}
Ojlen<-ToothGrowth[1:30,1] ## length by oj
Vclen<-ToothGrowth[31:60,1] ## length by Vc

t.test(Ojlen, Vclen, paired = TRUE)
```
Based on this test means in two supplements are not equal, as 95 percent confidence interval doesn't include 0 and t value is quite high.

Let's do the same, only based on suplement dose:

```{r}

dose05<-subset(ToothGrowth, dose == 0.5)[,1]
dose1<-subset(ToothGrowth, dose == 1)[,1]
dose2<-subset(ToothGrowth, dose == 2)[,1]


t.test(dose2,dose1, paired = TRUE)$conf
```
Doubled dozes and normal appears to differ.
```{r}
t.test(dose2,dose05,paired = TRUE)$conf
```

Difference between halfed and doubled dozes even stronger.

```{r}
t.test(dose1,dose05,paired = TRUE)$conf
```
And normal dozes and small doesn't appears to be same.

## Conslusion 

We made a assumptions (null hypothesizes), that teeth length doesn't based on type of supplement and its dose. However, t test showed, that all these hypothesizes were reject. Based on this information, we can assume that teeth length does base on the supplement type and its doze.